---
title: "theCLT"
author: "Alondra Garcia"
date: 'Summer 2022'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(lattice)
data("imagpop")
```

```{r}
KK_data <- imagpop$kkardashtemp
my1000 <- sample(KK_data, size = 1000, replace=T)
densityplot(my1000,main="original data")
print(mean(KK_data))
print(sd(KK_data))
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

No it's not unimodal, it's bimodal. There are two peaks and both peaks are the same size. There is 0 outliners in the plot. The mean is 49 and the standard deviation is 30.6

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
print(mean(x.avg))
print(sd(x.avg))
```

The mean for this data is 50.432 and the standard deviation is 26.7267782

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

It appears to me that the plot is not unimodal, the plot trimodal there are 3 peaks. Not all 3 peaks are the same, the peak in the middle is the largest peak and the other two are equal size to each other. There are no outliners. The mean for the graph is 50.3 and the standard deviation is 29.1

Do this again for 4 random samples

```{r}
numb = 4
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
print(mean(x.avg))
print(sd(x.avg))
densityplot(x.avg,main="sample size 4")
```

Then again for 9 random samples

```{r}
numb = 9
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
print(mean(x.avg))
print(sd(x.avg))
densityplot(x.avg,main="sample size 9")
```

then 16 random samples

```{r}
numb = 16
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
print(mean(x.avg))
print(sd(x.avg))
densityplot(x.avg,main="sample size 16")
```

This graph is unimodal, there is only 1 peak so there can not be a comparison in size. The mean for this graph is 50.6 and the standard deviation is 10.6

finally for 36 random samples.

```{r}
numb = 36
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
print(mean(x.avg))
print(sd(x.avg))
densityplot(x.avg,main="sample size 36")
```

This plot is unimodal and there is only 1 peak so there can't be a comparison in peaks. The mean for this graph is 50 and the standard deviation is 6.7

Write a summary paragraph describing what you observed and how it relates to the central limit theorem.

Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.

 The first plot is bimodal and appears to have a similar standard deviation and the mean to the next two plots. The mean and the standard deviation for the second and the third appear to be quite similar to each other. Than the fourth to sixth also appear to have similar standard deviation and means. The second and third plots are trimodal. The fourth to the sixth are unimodal. As we continue, our mean, stays relatively close to 50. Our standard deviation continues togo down as our sample gets bigger. It decreases from 29 to 6.7 and the CLT shows how the mean stays relatively the same as the sample size gets larger while the standard deviation gets smaller. 

Then submit the link to your github project  to canvas to complete this assignment.